---
title: "Week 2"
author: "Mumin Mohamed"
date:  "25/04/20"
output: 
  html_notebook: 
    fig_caption: yes
    toc: yes
 
---

This my first attempt at writing functions. I opted to use Markdown to note any
comments I have.

##Functions(Part 1)
###Function 1 

```{r}
add2 <- function(x,y){
  x+y
}
add2(8,2)

```
### Function 2 
```{r}
aboveN <-  function(x,n=10) {
  use <-  x>n
  print(x[use])
  paste('Cutoff Value is >',n)
}
aboveN(rnorm(20,10,4))
```

### Function 3
I forgot to add the '1:' part of 1:nc   inptut for the for loop. It makes sense 
and probably wont forget it it again. The for loop need a sequence to loop on. 
if  write just nc the for loop will assume as sequence of 1 and use that number
which would correspond with the last column
```{r}
#initial attempt failed
columnmeans <- function(y,removeNA=T){
  nc <- ncol(y)
  means <- numeric(nc)
  for(i in nc){
    means[i] <- mean(y[,i],na.rm=removeNA)
  }
  means
}
columnmeans(airquality)


#second attempt yipeee
columnmeans <- function(y,removeNA=T){
  nc <- ncol(y)
  means <- numeric(nc)
  for(i in 1:nc){
    means[i] <- mean(y[,i],na.rm=removeNA)
  }
  means
}

columnmeans(airquality)

```

***
##Functions(Part 2)

Lexical Scoping trial. 
```{r }
z <- 4
eq <-  function(x,y,z){
  x+y/z^2
}

```
My understanding was that if z is assigned to the global environment it would 
be searched for wihin the functions parent environment. This doesn't seem to be 
happening ...

```{r}
make.power <- function(n){
  pow <- function(x){
    x^n
  }
  pow
}
make.power(4)
pow(2)
```
So pow was created under make.power as the parent environment. unless i actively
assign to a value in the global environment , it  can't be used outside of the
make power function
```{r}
#attempt at using function to create a usable function in GE
make.power <- function(n){
  pow <- function(x){
    x^n
  }
  
}
pow<- make.power(3)
pow(4)

```
I couldnt assign to GE from within the function.


